### 2019-02-15 readme.Rmd
changes to qrbp, fix issue of not sampling across a dense matrix.

For a laugh, let's generate some quasirandom background points and plot them against the presence points. Here we are using the `quasirandom_covariates` method which tries to select quasirandom points across geographic and environmental space. The other working methods are `quasirandom` which just creates quasirandom points spatially, or `grid` which creates a regular grid at a set resolution - this is every similar to the grid design proposed by Warton & Shepard 2010.
```{r}
library(qrbp)
POdata <- species[species$Occurrence == 1,]
sp_sites <- POdata@coords
colnames(sp_sites) <- c("x","y")
bkpts_quasi <- generate_background_points(number_of_background_points = 1000,
                                    known_sites = sp_sites,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    method = 'quasirandom')
```

For a laugh, let's generate some quasirandom background points and plot them against the presence points
```{r}
bkpts_grid <- generate_background_points(known_sites = sp_sites,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    resolution = 16000, # this needs to be relative to raster resolution - this is about half the input resolution of the raster.
                                    method = 'grid')
```

@@

```{r,warning=FALSE,error=FALSE,message=FALSE}
library(mgcv)
bkpts_quasi <- generate_background_points(number_of_background_points = 20000,
                                    known_sites = POdata@coords,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    method = 'quasirandom')
fm <- gam(presence/weights ~ s(elevation) +
              s(precipitation) +
              s(temperature) +
              s(vegetation),
              weights = weights,
              data = bkpts_quasi,
              family = poisson())

@@

p_cell <- p*(res(preds)[1]*res(preds)[2])/4 # resolution of raster changes with bkpts_quasi - need to remember that.

>>>>

For a laugh, let's generate some quasirandom background points and plot them against the presence points. Here we are using the `quasirandom_covariates` method which tries to select quasirandom points across geographic and environmental space. The other working methods are `quasirandom` which just creates quasirandom points spatially, or `grid` which creates a regular grid at a set resolution - this is every similar to the grid design proposed by Warton & Shepard 2010.
```{r}
library(qrbp)
POdata <- species[species$Occurrence == 1,]
sp_sites <- POdata@coords
colnames(sp_sites) <- c("x","y")
bkpts_quasi <- generate_background_points(number_of_background_points = 1000,
                                    known_sites = sp_sites,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    method = 'single_species_quasi')
```

For a laugh, let's generate some quasirandom background points and plot them against the presence points
```{r}
bkpts_grid <- generate_background_points(known_sites = sp_sites,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    resolution = 16000, # this needs to be relative to raster resolution - this is about half the input resolution of the raster.
                                    method = 'single_species_grid')
```

@@

```{r,warning=FALSE,error=FALSE,message=FALSE}
library(mgcv)
bkpts_quasi <- generate_background_points(number_of_background_points = 5000,
                                    known_sites = POdata@coords,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    method = 'single_species_quasi')
fm <- gam(presence/weights ~ s(elevation) +
              s(precipitation) +
              s(temperature) +
              s(vegetation),
              weights = weights,
              data = bkpts_quasi,
              family = poisson())

@@

p_cell <- p*(res(preds)[1]*res(preds)[2])/1000 # resolution of raster changes with bkpts_quasi - need to remember that. 
cellStats(p_cell,sum)
